---
title: "Reprocessing PFTC7 fluxes"
format: gfm
author: Joseph Gaudard
date: today
bibliography: /home/jga051/Dropbox/PhD/biblio_phd_zot.bib
csl: /home/jga051/Documents/01_PhD/apa-old-doi-prefix.csl
---

```{r}
#| include: FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(tidyverse.quiet = TRUE)
```

# Importing and reading the files

```{r}
#| label: osf-import
#| message: FALSE
my_packages <- c(
  "dataDownloader",
  "tidyverse",
  "licoread",
  "fluxible",
  "here"
)

lapply(my_packages, library, character.only = TRUE)

sites <- c(1:5)

files <- paste0("LI7500_Site ", sites, ".zip")

lapply(files,
       get_file,
       node = "hk2cy",
       remote_path = "raw_data/x_raw_ecosystem_fluxes/LI7500",
       path = "pftc7_raw_data")

files_zip <- paste0("pftc7_raw_data/", files)

lapply(files_zip,
       unzip,
       exdir = "pftc7_raw_data/LI7500")

# ok so those files are full of things we don't want...
not_use <- c("not used", "old")
files_remove <- files |>
  str_remove(".zip") |>
  rep(2) |>
  paste0("pftc7_raw_data/LI7500/", . = _, "/", not_use) |>
  append(
    c("pftc7_raw_data/LI7500/__MACOSX",
      "pftc7_raw_data/LI7500/LI7500_Site 4/4_2600_west_2_night_resp-2023-12-16T200310.txt") # this file is empty and makes import crash
  )

unlink(here(files_remove), recursive = TRUE)
```

```{r}
#| label: reading
#| message: FALSE


pftc7_raw_data <- import7500("pftc7_raw_data/LI7500", version = "post2023")

pftc7_data <- pftc7_raw_data |>
  mutate(
  f_fluxid_temp = str_replace_all(f_fluxid, c(" " = "_", "__" = "_")), # name convention...
  replicate = case_when(
    str_detect(f_fluxid_temp, "_redo") ~ 2,
    .default = 1
  ),
  f_fluxid_temp = str_remove_all(f_fluxid_temp, "_redo")
  ) |>
  separate_wider_delim(f_fluxid_temp, "_", names = c(
    "site_id",
    "elevation_m_asl",
    "aspect",
    "plot_id",
    "day_night",
    "flux_type"
    ),
    too_many = "drop"
  ) |>
  mutate(
    flux_type = str_extract(flux_type, "^(\\w+)(?=-)|^(\\w+)(?=\\.txt$)|^\\w"), # getting rid of the rest
    flux_type = str_replace_all(flux_type, "r$", "resp"),
    site_id = as.double(site_id),
    elevation_m_asl = as.double(elevation_m_asl),
    plot_id = as.double(plot_id)
  )

pftc7_data |>
  distinct(flux_type)

```

# Processing

## CO~2~

Wet air correction:
```{r}
#| label: wetair_co2
pftc7_data <- flux_drygas(pftc7_data, `CO2 (umol/mol)`, `H2O (mmol/mol)`)
```

### Exponential model

Fitting the model presented in @zhaoCalculationDaytimeCO22018 .
```{r}
#| label: fitting_exp_co2
#| message: FALSE
#| warning: FALSE
pftc7_fits_exp_co2 <- flux_fitting(pftc7_data,
                                   f_conc = `CO2 (umol/mol)_dry`,
                                   fit_type = "exp_zhao18",
                                   start_cut = 0,
                                   end_cut = 0)
```

Using `fluxible::flux_quality` to assess the quality of the dataset.
```{r}
#| label: flags_exp_co2
pftc7_flags_exp_co2 <- flux_quality(pftc7_fits_exp_co2,
                                    f_conc = `CO2 (umol/mol)_dry`,
                                    rsquared_threshold = 0.5)
```

```{r}
#| label: plotting_exp_co2
#| eval: FALSE

pftc7_flags_exp_co2 |>
  flux_plot(f_conc = `CO2 (umol/mol)_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 500,
            f_ylim_lower = 350,
            y_text_position = 430,
            # f_facetid = c("f_fluxid", "filename"),
            f_plotname = "pftc7_exp_co2")

```

Now let's calculate the fluxes with `fluxible::flux_calc`.
```{r}
#| label: calc_exp_co2

pftc7_fluxes_exp_co2 <- flux_calc(pftc7_flags_exp_co2,
                                  slope_col = f_slope_corr,
                                  temp_air_col = `Temperature (C)`,
                                  setup_volume = 2197,
                                  atm_pressure = pressure_atm,
                                  plot_area = 1.44,
                                  conc_unit = "ppm",
                                  flux_unit = "umol/m2/s",
                                  cols_keep = c(
                                    "Date", "Time", "f_quality_flag",
                                    "site_id", "elevation_m_asl", "aspect",
                                    "plot_id", "day_night", "flux_type",
                                    "replicate"
                                  ))

```

### Linear model

```{r}
#| label: fitting_lin_co2
#| message: FALSE
#| warning: FALSE
pftc7_fits_lin_co2 <- flux_fitting(pftc7_data,
                                   f_conc = `CO2 (umol/mol)_dry`,
                                   fit_type = "linear",
                                   start_cut = 0,
                                   end_cut = 0)
```

Using `fluxible::flux_quality` to assess the quality of the dataset.
```{r}
#| label: flags_lin_co2
pftc7_flags_lin_co2 <- flux_quality(pftc7_fits_lin_co2,
                                    f_conc = `CO2 (umol/mol)_dry`,
                                    rsquared_threshold = 0.5)
```



Now let's calculate the fluxes with `fluxible::flux_calc`.
```{r}
#| label: calc_lin_co2

pftc7_fluxes_lin_co2 <- flux_calc(pftc7_flags_lin_co2,
                                  slope_col = f_slope_corr,
                                  temp_air_col = `Temperature (C)`,
                                  setup_volume = 2197,
                                  atm_pressure = pressure_atm,
                                  plot_area = 1.44,
                                  conc_unit = "ppm",
                                  flux_unit = "umol/m2/s",
                                  cols_keep = c(
                                    "Date", "Time", "f_quality_flag",
                                    "site_id", "elevation_m_asl", "aspect",
                                    "plot_id", "day_night", "flux_type",
                                    "replicate"
                                  ))

```

## H~2~O

Wet air correction:
```{r}
#| label: wetair_co2
pftc7_data <- flux_drygas(pftc7_data, `H2O (mmol/mol)`, `H2O (mmol/mol)`)
```

### Exponential model

Fitting the model presented in @zhaoCalculationDaytimeCO22018 .
```{r}
#| label: fitting_exp_h2o
#| message: FALSE
#| warning: FALSE
pftc7_fits_exp_h2o <- flux_fitting(pftc7_data,
                                   f_conc = `H2O (mmol/mol)`,
                                   fit_type = "exp_zhao18",
                                   start_cut = 0,
                                   end_cut = 0)
```

Using `fluxible::flux_quality` to assess the quality of the dataset.
```{r}
#| label: flags_exp_h2o
pftc7_flags_exp_h2o <- flux_quality(pftc7_fits_exp_h2o,
                                    f_conc = `H2O (mmol/mol)`,
                                    rsquared_threshold = 0.5,
                                    ambient_conc = 20,
                                    error = 10)
```

```{r}
#| label: plotting_exp_h2o
#| eval: FALSE

pftc7_flags_exp_h2o |>
  flux_plot(f_conc = `H2O (mmol/mol)`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 40,
            f_ylim_lower = 0,
            y_text_position = 15,
            # f_facetid = c("f_fluxid", "filename"),
            f_plotname = "pftc7_exp_h2o")

```

Now let's calculate the fluxes with `fluxible::flux_calc`.
```{r}
#| label: calc_exp_h2o

pftc7_fluxes_exp_h2o <- flux_calc(pftc7_flags_exp_h2o,
                                  slope_col = f_slope_corr,
                                  temp_air_col = `Temperature (C)`,
                                  setup_volume = 2197,
                                  atm_pressure = pressure_atm,
                                  plot_area = 1.44,
                                  conc_unit = "mmol/mol",
                                  flux_unit = "mmol/m2/s",
                                  cols_keep = c(
                                    "Date", "Time", "f_quality_flag",
                                    "site_id", "elevation_m_asl", "aspect",
                                    "plot_id", "day_night", "flux_type",
                                    "replicate"
                                  ))

```

### Linear model

```{r}
#| label: fitting_lin_h2o
#| message: FALSE
#| warning: FALSE
pftc7_fits_lin_h2o <- flux_fitting(pftc7_data,
                                   f_conc = `H2O (mmol/mol)`,
                                   fit_type = "linear",
                                   start_cut = 0,
                                   end_cut = 0)
```

Using `fluxible::flux_quality` to assess the quality of the dataset.
```{r}
#| label: flags_lin_h2o
pftc7_flags_lin_h2o <- flux_quality(pftc7_fits_lin_h2o,
                                    f_conc = `H2O (mmol/mol)`,
                                    rsquared_threshold = 0.5,
                                    ambient_conc = 20,
                                    error = 10)
```




Now let's calculate the fluxes with `fluxible::flux_calc`.
```{r}
#| label: calc_lin_h2o

pftc7_fluxes_lin_h2o <- flux_calc(pftc7_flags_lin_h2o,
                                  slope_col = f_slope_corr,
                                  temp_air_col = `Temperature (C)`,
                                  setup_volume = 2197,
                                  atm_pressure = pressure_atm,
                                  plot_area = 1.44,
                                  conc_unit = "mmol/mol",
                                  flux_unit = "mmol/m2/s",
                                  cols_keep = c(
                                    "Date", "Time", "f_quality_flag",
                                    "site_id", "elevation_m_asl", "aspect",
                                    "plot_id", "day_night", "flux_type",
                                    "replicate"
                                  ))

```

# Comparison


Adjusting to PFTC7 naming convention
```{r}
#| label: fluxible-format_co2

pftc7_fluxible_fluxes_co2 <- pftc7_fluxes_exp_co2 |>
  bind_rows(pftc7_fluxes_lin_co2) |>
  mutate(
    flux_category = "Carbon",
    flux_type = case_when(
      flux_type == "resp" & day_night == "day" ~ "resp_day",
      flux_type == "resp" & day_night == "night" ~ "resp_night",
      flux_type == "photo" ~ "nee",
      .default = flux_type
    )
  )

pftc7_fluxible_fluxes_h2o <- pftc7_fluxes_exp_h2o |>
  bind_rows(pftc7_fluxes_lin_h2o) |>
  mutate(
    flux_category = "Water",
    flux_type = case_when(
      flux_type == "resp" & day_night == "day" ~ "evap_day",
      flux_type == "resp" & day_night == "night" ~ "evap_night",
      flux_type == "photo" ~ "evapotrans",
      .default = flux_type
    )
  )

# keeping the redo when there is a redo
pftc7_fluxible_fluxes <- bind_rows(pftc7_fluxible_fluxes_co2, pftc7_fluxible_fluxes_h2o) |>
  arrange(desc(replicate)) |>
  distinct(site_id, elevation_m_asl, aspect, plot_id, day_night, flux_type, flux_category, f_model, .keep_all = TRUE)
```

Downloading and adjusting published data
```{r}
#| label: pftc7-fluxes_co2

get_file("hk2cy",
         "x_ecosystem_fluxes",
         "x_PFTC7_clean_ecosystem_fluxes_2023.csv",
         "pftc7_raw_data")

pftc7_published_fluxes <- read_csv("pftc7_raw_data/x_PFTC7_clean_ecosystem_fluxes_2023.csv")

pftc7_published_fluxes <- pftc7_published_fluxes |>
  filter(device == "LI-7500")

```

Gathering the data
```{r}
#| label: gathering-co2

pfct7_comparison <- pftc7_published_fluxes |>
  left_join(pftc7_fluxible_fluxes, by = join_by(site_id, elevation_m_asl, aspect, plot_id, day_night, flux_type, flux_category))

```

```{r}
#| label: figure_h2o
#| echo: FALSE
#| fig-cap: "Comparison of fluxes calculated with fluxible and published PFTC7 data paper."
#| message: FALSE
#| warning: FALSE
#| fig-width: 8
#| fig-height: 8 

pfct7_comparison |>
  ggplot(aes(f_flux, flux_value, color = f_model)) +
  theme_bw() +
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  geom_smooth(
    method = "lm"
  ) +
  facet_wrap(. ~ flux_type, ncol = 2, scales = "free") +
  labs(
    title = "Reprocessing of PFTC7 flux data",
    x = "Fluxes calculated with Fluxible (exp_zhao18 and linear model)",
    y = "Fluxes as published in the data paper",
    color = "Fluxible model"
  ) 

```

```{r}
#| label: cleaning
#| eval: false
unlink(here("pftc7_raw_data"),
       recursive = TRUE)
```

