---
title: "Reprocessing PFTC5 fluxes"
output: gfm
author: Joseph Gaudard
date: today
bibliography: /home/jga051/Dropbox/PhD/biblio_phd_zot.bib
csl: /home/jga051/Documents/01_PhD/apa-old-doi-prefix.csl
---

```{r}
#| include: FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(tidyverse.quiet = TRUE)
```

This report aims at reproducing the ecosystem fluxes (CO~2~ and H~2~O) processing presented in @halbritterPlantTraitVegetation2024.


# Importing and reading the files

First, we import the data from OSF with `dataDownloader::get_file`.

```{r}
#| label: osf-import
#| message: FALSE
library(dataDownloader)

get_file("gs8u6",
         "rawData/raw_c-flux",
         "rawC-flux.zip",
         "pftc5")

unzip("pftc5/rawC-flux.zip",
      exdir = "pftc5/rawC-flux")
```

Then we import the data with `licoread::import7500`.
```{r}
#| label: reading
#| message: FALSE
library(licoread)
library(tidyverse)
pftc5_data_raw <- import7500(
  "pftc5/rawC-flux/rawData/raw_tent-flux",
  plotinfo = c("site", "treatment", "date", "plot_id", "trial")
)

pftc5_data_raw <- pftc5_data_raw |>
  rename(filename = "f_fluxid") # f_fluxid will be re created by flux_match

```

<!-- The `licoread::import7500` function provides `f_fluxid`, `f_start` and `f_end`, meaning we could skip `fluxible::flux_match`. -->
To reproduce the similar flux by flux cutting done during the PFTC5, we will  recreate the `field_record` input.
We can use the `t_start` and `t_finish` columns in the clean data for that, since they correspond to the cuts the team decided to apply.
Note that this is also an example of how fluxible can be used to process data in a non homogenous way, would that be necessary.

```{r}
#| label: reformat

# downloading clean data
get_file("gs8u6",
         "c-flux",
         "PFTC3_Puna_PFTC5_Peru_2018_2020_Cflux.csv",
         "pftc5")

pftc5_published_fluxes_co2 <- read_csv(
  "pftc5/PFTC3_Puna_PFTC5_Peru_2018_2020_Cflux.csv",
  show_col_types = FALSE # quiet!
)

pftc5_published_fluxes_co2 <- pftc5_published_fluxes_co2 |>
  mutate(
    date = ymd(paste(year, month, day)),
    replicate = case_when(
      flux == "Reco" ~ 1,
      flux == "NEE" ~ 1,
      flux == "NEE1" ~ 2,
      flux == "NEE2" ~ 3,
      flux == "NEE3" ~ 4
    ),
    flux = case_when(
      flux == "Reco" ~ "Reco",
      flux == "NEE" ~ "NEE",
      flux == "NEE1" ~ "NEE",
      flux == "NEE2" ~ "NEE",
      flux == "NEE3" ~ "NEE"
    )
  )

# normally the same cuts should have been applied to CO2 and H2O
pftc5_cuts <- pftc5_published_fluxes_co2 |>
  select(date, flux, replicate, site, treatment, plot_id, t_start, t_finish)

# t_start and t_finish are relative time
# we need to fetch datetime from the raw data

pftc5_record <- pftc5_data_raw |>
  mutate(
    plot_id = as.integer(str_extract(plot_id, "\\d+")),
    flux = case_when(
      trial == "r" ~ "Reco",
      trial == "p" ~ "NEE",
      trial == "p1" ~ "NEE",
      trial == "p2" ~ "NEE",
      trial == "p3" ~ "NEE"
    ),
    replicate = case_when(
      trial == "r" ~ 1,
      trial == "p" ~ 1,
      trial == "p1" ~ 2,
      trial == "p2" ~ 3,
      trial == "p3" ~ 4
    ),
    date = as_date(f_datetime)
  ) |>
  select(f_start, date, flux, site, treatment, plot_id, replicate) |>
  distinct() |>
  drop_na(flux) |>
  left_join(pftc5_cuts,
            by = join_by(date, flux, site, treatment, plot_id, replicate)) |>
  mutate(
    start = f_start + t_start,
    end = f_start + t_finish
  ) |>
  select(!c(f_start, t_start, t_finish)) |> # to avoid confusion
  arrange(start)

# Now the meta data are in pftc5_record,
# we remove them from pftc5_data to avoid confusion
# flux match crashes if columns are both in raw data and record
# this will be corrected in next version

pftc5_data <- pftc5_data_raw |>
  select(!c(site, treatment, plot_id, trial, date, f_start, f_end))
```

# Processing with fluxible
<!-- Since the `licoread::import7500` already provides `f_fluxid`, `f_start` and `f_end`, we can skip `fluxible::flux_match` and directly fit with `fluxible::flux_fitting`. -->
We will fit both the linear and exponential model for comparison purpose.

```{r}
#| label: match
#| message: FALSE
#| warning: FALSE
library(fluxible)
pftc5_match <- flux_match(pftc5_data,
                          pftc5_record,
                          f_datetime = f_datetime,
                          start_col = start,
                          end_col = end)
```

## CO~2~

Wet air correction:
```{r}
#| label: wetair_co2
pftc5_match <- flux_drygas(pftc5_match, `CO2 umol/mol`, `H2O mmol/mol`)
```

### Exponential model

Fitting the model presented in @zhaoCalculationDaytimeCO22018 .
```{r}
#| label: fitting_exp_co2
#| message: FALSE
#| warning: FALSE
pftc5_fits_exp_co2 <- flux_fitting(pftc5_match,
                                   f_conc = `CO2 umol/mol_dry`,
                                   fit_type = "exp_zhao18",
                                   start_cut = 0,
                                   end_cut = 0)
```

Using `fluxible::flux_quality` to assess the quality of the dataset.
```{r}
#| label: flags_exp_co2
pftc5_flags_exp_co2 <- flux_quality(pftc5_fits_exp_co2,
                                    f_conc = `CO2 umol/mol_dry`,
                                    rsquared_threshold = 0.5)
```


Then plotting (in an external file) for a visual check.
Because of the number of data, we will do it per site to make it lighter.
```{r}
#| label: plotting_exp_co2
#| eval: FALSE

pftc5_flags_exp_co2 <- pftc5_flags_exp_co2 |>
  drop_na(filename)
# some filename are NA because the start provided does not fall
# exactly on a row with concentration

pftc5_flags_exp_co2 |>
  dplyr::filter(site == "ACJ") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 500,
            f_ylim_lower = 350,
            y_text_position = 430,
            # f_facetid = c("f_fluxid", "filename"),
            f_plotname = "ACJ_plot_exp_co2")

pftc5_flags_exp_co2 |>
  dplyr::filter(site == "PIL") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 500,
            f_ylim_lower = 350,
            y_text_position = 430,
            f_plotname = "PIL_plot_exp_co2")

pftc5_flags_exp_co2 |>
  dplyr::filter(site == "QUE") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 500,
            f_ylim_lower = 350,
            y_text_position = 430,
            f_plotname = "QUE_plot_exp_co2")

pftc5_flags_exp_co2 |>
  dplyr::filter(site == "TRE") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 500,
            f_ylim_lower = 350,
            y_text_position = 430,
            f_plotname = "TRE_plot_exp_co2")

pftc5_flags_exp_co2 |>
  dplyr::filter(site == "WAY") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 500,
            f_ylim_lower = 350,
            y_text_position = 430,
            f_plotname = "WAY_plot_exp_co2")


```

Now let's calculate the fluxes with `fluxible::flux_calc`.
```{r}
#| label: calc_exp_co2
pftc5_fluxes_exp_co2 <- flux_calc(pftc5_flags_exp_co2,
                                  slope_col = f_slope_corr,
                                  temp_air_col = Temperature,
                                  setup_volume = 2197,
                                  atm_pressure = pressure_atm,
                                  plot_area = 1.44,
                                  conc_unit = "ppm",
                                  flux_unit = "umol/m2/s",
                                  cols_keep = c(
                                    "site", "treatment", "date", "plot_id",
                                    "flux", "replicate"
                                  ))
```

### Linear model

Fitting a linar model:
```{r}
#| label: fitting_lm_co2
#| message: FALSE
#| warning: FALSE
pftc5_fits_lm_co2 <- flux_fitting(pftc5_match,
                                  f_conc = `CO2 umol/mol_dry`,
                                  fit_type = "linear",
                                  start_cut = 0,
                                  end_cut = 0)
```

Using `fluxible::flux_quality` to assess the quality of the dataset:
```{r}
#| label: flags_lm_co2
pftc5_flags_lm_co2 <- flux_quality(pftc5_fits_lm_co2,
                                   f_conc = `CO2 umol/mol_dry`,
                                   rsquared_threshold = 0.5)
```


<!-- Then plotting (in an external file) for a visual check: -->
```{r}
#| label: plotting_lm_co2
#| eval: FALSE
#| include: FALSE
pftc5_flags_lm_co2 |>
  dplyr::filter(site == "ACJ") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "ACJ_plot_lm_co2")

pftc5_flags_lm_co2 |>
  dplyr::filter(site == "PIL") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "PIL_plot_lm_co2")

pftc5_flags_lm_co2 |>
  dplyr::filter(site == "QUE") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "QUE_plot_lm_co2")

pftc5_flags_lm_co2 |>
  dplyr::filter(site == "TRE") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "TRE_plot_lm_co2")

pftc5_flags_lm_co2 |>
  dplyr::filter(site == "WAY") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "WAY_plot_lm_co2")

pftc5_flags_lm_co2 |>
  dplyr::filter(f_quality_flag == "zero") |>
  flux_plot(f_conc = `CO2 umol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 500,
            f_ylim_lower = 350,
            y_text_position = 450,
            f_plotname = "zero_plot_lm_co2")
```

Flux calculation:
```{r}
#| label: calc_lm_co2
pftc5_fluxes_lm_co2 <- flux_calc(pftc5_flags_lm_co2,
                                 slope_col = f_slope_corr,
                                 temp_air_col = Temperature,
                                 setup_volume = 2197,
                                 atm_pressure = pressure_atm,
                                 plot_area = 1.44,
                                 conc_unit = "ppm",
                                 flux_unit = "umol/m2/s",
                                 cols_keep = c(
                                   "site", "treatment", "date", "plot_id",
                                   "flux", "replicate"
                                 ))
```

## H~2~O

We need to change the denomination of the fluxes, because now we work with H~2~O.
Other than that, it is the same procedure and the same functions.

```{r}
#| label: match_h2o
pftc5_match_h2o <- pftc5_match |>
  mutate(
    flux = str_replace_all(flux, c(
      "NEE" = "ET",
      "Reco" = "E"
    ))
  )
```


Wet air correction:
```{r}
#| label: wetair_h2o
pftc5_match_h2o <- flux_drygas(pftc5_match_h2o, `H2O mmol/mol`, `H2O mmol/mol`)
```



### Exponential model

Fitting the model presented in @zhaoCalculationDaytimeCO22018.
```{r}
#| label: fitting_exp_h2o
#| message: FALSE
#| warning: FALSE
pftc5_fits_exp_h2o <- flux_fitting(pftc5_match_h2o,
                                   f_conc = `H2O mmol/mol_dry`,
                                   fit_type = "exp_zhao18",
                                   start_cut = 0,
                                   end_cut = 0)
```

Using `fluxible::flux_quality` to assess the quality of the dataset:
```{r}
#| label: flags_exp_h2o
pftc5_flags_exp_h2o <- flux_quality(pftc5_fits_exp_h2o,
                                    f_conc = `H2O mmol/mol_dry`,
                                    rsquared_threshold = 0.5,
                                    ambient_conc = 20, # the default is for CO2
                                    error = 10)
```


Then plotting (in an external file) for a visual check:
```{r}
#| label: plotting_exp_h2o
#| eval: FALSE
pftc5_flags_exp_h2o |>
  dplyr::filter(site == "ACJ") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 40,
            f_ylim_lower = 0,
            y_text_position = 20,
            f_plotname = "ACJ_plot_exp_h2o")

pftc5_flags_exp_h2o |>
  dplyr::filter(site == "PIL") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 40,
            f_ylim_lower = 0,
            y_text_position = 20,
            f_plotname = "PIL_plot_exp_h2o")

pftc5_flags_exp_h2o |>
  dplyr::filter(site == "QUE") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 40,
            f_ylim_lower = 0,
            y_text_position = 20,
            f_plotname = "QUE_plot_exp_h2o")

pftc5_flags_exp_h2o |>
  dplyr::filter(site == "TRE") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 40,
            f_ylim_lower = 0,
            y_text_position = 20,
            f_plotname = "TRE_plot_exp_h2o")

pftc5_flags_exp_h2o |>
  dplyr::filter(site == "WAY") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 40,
            f_ylim_lower = 0,
            y_text_position = 20,
            f_plotname = "WAY_plot_exp_h2o")


```

Flux calculations:
```{r}
#| label: calc_exp_h2o
pftc5_fluxes_exp_h2o <- flux_calc(pftc5_flags_exp_h2o,
                                  slope_col = f_slope_corr,
                                  temp_air_col = Temperature,
                                  setup_volume = 2197,
                                  atm_pressure = pressure_atm,
                                  plot_area = 1.44,
                                  conc_unit = "mmol/mol",
                                  flux_unit = "mmol/m2/s",
                                  cols_keep = c(
                                    "site", "treatment", "date", "plot_id",
                                    "flux", "replicate"
                                  ))
```

### Linear model

Fitting a linar model:
```{r}
#| label: fitting_lm_h2o
#| message: FALSE
#| warning: FALSE
pftc5_fits_lm_h2o <- flux_fitting(pftc5_match_h2o,
                                  f_conc = `H2O mmol/mol_dry`,
                                  fit_type = "linear",
                                  start_cut = 0,
                                  end_cut = 0)
```

Using `fluxible::flux_quality` to assess the quality of the dataset:
```{r}
#| label: flags_lm_h2o
pftc5_flags_lm_h2o <- flux_quality(pftc5_fits_lm_h2o,
                                   f_conc = `H2O mmol/mol_dry`,
                                   rsquared_threshold = 0.5,
                                   ambient_conc = 40, # the default is for CO2
                                   error = 20)
```



<!-- Then plotting (in an external file) for a visual check: -->
```{r}
#| label: plotting_lm_h2o
#| eval: FALSE
#| include: FALSE
pftc5_flags_lm_h2o |>
  dplyr::filter(site == "ACJ") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "ACJ_plot_lm_h2o")

pftc5_flags_lm_h2o |>
  dplyr::filter(site == "PIL") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "PIL_plot_lm_h2o")

pftc5_flags_lm_h2o |>
  dplyr::filter(site == "QUE") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "QUE_plot_lm_h2o")

pftc5_flags_lm_h2o |>
  dplyr::filter(site == "TRE") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "TRE_plot_lm_h2o")

pftc5_flags_lm_h2o |>
  dplyr::filter(site == "WAY") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_plotname = "WAY_plot_lm_h2o")

pftc5_flags_lm_h2o |>
  dplyr::filter(f_quality_flag == "zero") |>
  flux_plot(f_conc = `H2O mmol/mol_dry`,
            print_plot = FALSE,
            output = "longpdf",
            f_ylim_upper = 500,
            f_ylim_lower = 350,
            y_text_position = 450,
            f_plotname = "zero_plot_lm_h2o")
```

Flux calculations:
```{r}
#| label: calc_lm_h2o
pftc5_fluxes_lm_h2o <- flux_calc(pftc5_flags_lm_h2o,
                                 slope_col = f_slope_corr,
                                 temp_air_col = Temperature,
                                 setup_volume = 2197,
                                 atm_pressure = pressure_atm,
                                 plot_area = 1.44,
                                 conc_unit = "mmol/mol",
                                 flux_unit = "mmol/m2/s",
                                 cols_keep = c(
                                   "site", "treatment", "date", "plot_id",
                                   "flux", "replicate"
                                 ))
```



# Comparison

## CO~2~

Let's format the fluxible fluxes in a similar way.
```{r}
#| label: fluxible-format_co2
pftc5_fluxible_fluxes_co2 <- pftc5_fluxes_exp_co2 |>
  bind_rows(pftc5_fluxes_lm_co2) |>
  mutate(
    fluxible_flux = -f_flux # the opposite convention was used for PFTC5
  ) |>
  drop_na(flux) # removing amb measurements
```

<!-- Now download and format PFTC5 fluxes. -->
<!-- In the clean data on OSF, both linear and nls fluxes are available.
Which one to choose is not explicit (but I am tired, do not quote me on that), so we will just take the one with the lowest aic for now. -->
```{r}
#| label: pftc5-fluxes_co2


pftc5_published_fluxes_co2 <- pftc5_published_fluxes_co2 |>
  pivot_longer(
    c(linear_model, nls_model),
    values_to = "published_fluxes",
    names_to = "model"
  )
```

Putting them together:
```{r}
#| label: gathering_co2
pftc5_fluxes_comparison_co2 <- left_join(pftc5_published_fluxes_co2,
                                         pftc5_fluxible_fluxes_co2,
                                         by = join_by(date, flux,
                                                      site, treatment,
                                                      plot_id, replicate),
                                         relationship = "many-to-many")
```

```{r}
#| label: figure_co2
#| echo: FALSE
#| fig-cap: "Comparison of CO2 fluxes calculated with fluxible and published in Halbritter et al (2024)."
#| message: FALSE
#| warning: FALSE
#| fig-width: 8
#| fig-height: 8

pftc5_fluxes_comparison_co2 |>
  ggplot(aes(fluxible_flux, published_fluxes, color = model)) +
  theme_bw() +
  scale_color_manual(values = c(
        nls_model = "#0c9f0b",
        linear_model = "#bf28bd")
  ) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  geom_smooth(
    method = "lm"
  ) +
  facet_grid(f_model ~ flux, scales = "free") +
  labs(
    title = "Reprocessing of PFTC5 CO~2~ flux data",
    x = "Fluxes calculated with Fluxible (exp_zhao18 and linear model respectively)",
    y = "Fluxes as published in the data paper",
    color = "Model (PFTC5)"
  ) 
  # geom_text(aes(label = f_fluxid), vjust = -0.5)
```


## H~2~O

Let's format the fluxible fluxes in a similar way.
```{r}
#| label: fluxible-format_h2o
pftc5_fluxible_fluxes_h2o <- pftc5_fluxes_exp_h2o |>
  bind_rows(pftc5_fluxes_lm_h2o) |>
  rename(
    fluxible_flux = "f_flux"
  ) |>
  drop_na(flux) # removing amb measurements
```

<!-- Now download and format PFTC5 fluxes. -->
<!-- In the clean data on OSF, both linear and nls fluxes are available.
Which one to choose is not explicit (but I am tired, do not quote me on that), so we will just take the one with the lowest aic for now. -->
Importing the published dataset:
```{r}
#| label: pftc5-fluxes_h2o

get_file("gs8u6",
         "c-flux",
         "PFTC3_Puna_PFTC5_Peru_2018_2020_wflux.csv",
         "ex_data/li7500")

pftc5_published_fluxes_h2o <- read_csv(
  "ex_data/li7500/PFTC3_Puna_PFTC5_Peru_2018_2020_wflux.csv",
  show_col_types = FALSE # quiet!
)

pftc5_published_fluxes_h2o <- pftc5_published_fluxes_h2o |>
  mutate(
    date = ymd(paste(year, month, day)),
    replicate = case_when(
      flux == "E" ~ 1,
      flux == "ET" ~ 1,
      flux == "ET1" ~ 2,
      flux == "ET2" ~ 3,
      flux == "ET3" ~ 4
    ),
    flux = case_when(
      flux == "E" ~ "E",
      flux == "ET" ~ "ET",
      flux == "ET1" ~ "ET",
      flux == "ET2" ~ "ET",
      flux == "ET3" ~ "ET"
    )
  )

pftc5_published_fluxes_h2o <- pftc5_published_fluxes_h2o |>
  pivot_longer(
    c(linear_model, nls_model),
    values_to = "published_fluxes",
    names_to = "model"
  )
```

Putting them together:
```{r}
#| label: gathering_h2o
pftc5_fluxes_comparison_h2o <- left_join(pftc5_published_fluxes_h2o,
                                         pftc5_fluxible_fluxes_h2o,
                                         by = join_by(date, flux,
                                                      site, treatment,
                                                      plot_id, replicate),
                                         relationship = "many-to-many")
```

```{r}
#| label: figure_h2o
#| echo: FALSE
#| fig-cap: "Comparison of H~2~O fluxes calculated with fluxible and published in Halbritter et al (2024)."
#| message: FALSE
#| warning: FALSE
#| fig-width: 8
#| fig-height: 8 
pftc5_fluxes_comparison_h2o |>
  ggplot(aes(fluxible_flux, published_fluxes, color = model)) +
  theme_bw() +
  scale_color_manual(values = c(
        nls_model = "#0c9f0b",
        linear_model = "#bf28bd")
  ) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  geom_smooth(
    method = "lm"
  ) +
  facet_grid(f_model ~ flux, scales = "free") +
  labs(
    title = "Reprocessing of PFTC5 H2O flux data",
    x = "Fluxes calculated with Fluxible (exp_zhao18 and linear model respectively)",
    y = "Fluxes as published in the data paper",
    color = "Model (PFTC5)"
  ) 
  # geom_text(aes(label = f_fluxid), vjust = -0.5)
```

## Possible explanation for the differences

- Problem detected: some measurements overlap. It means the logger was off at some point, or the cutting in the clean data has errors.
- Since the nls_model is an exponential model without linear term, it gives unrealistic estimates when fitted to a flux that has no curvature [@huppiRestrictingNonlinearityParameter2018; @pedersenComprehensiveApproachSoilatmosphere2010a]. Fluxible solves this issue by using the model presented in @zhaoCalculationDaytimeCO22018, which is also an exponential but contains a linear term allowing it to fit linear data.
- The fluxes with hight published values and zero with fluxible are good examples of the behaviour of the nls model with linear data. Looking at the plot, it is evident that those fluxes are close to zero. In fluxible, they get flagged for as "bad fit", but since there is no change of concentration over time they get replaced by zero instead of getting discarded.
- Possible explanation for the over estimation of the exponential model in fluxible compared to the linear model can be found in @kutzbachCO2FluxDetermination2007 .
- At this point I don't have a good hypothesis for the slight over estimation with fluxible when using a linear model. If some of those fluxes are the overlapping ones, then they were fitted on a shorter time or they included data from another measurement.

<!-- ## Investigation of differences -->

```{r}
#| label: cleaning
#| include: FALSE
library(here)
unlink(here("R", "data_cleaning_and_prep", "pftc5"),
       recursive = TRUE)
```

### References
